---
title: "MB19 Sprint"
author: "Eden Axelrad"
date: '2022-12-22'
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
---

```{r setup, include=FALSE}

# Load required libraries
library(readxl)
library(tidyverse)
library(lubridate)
library(gt)
library(gtExtras)


# Read in data
MB19 <- read_excel("Data/Moonboard 2019.xlsx", sheet = "Tracker") %>%
  select(1:9) %>%
  mutate(Date = as.Date(Date, format = "%Y-%m-%d"))

MB19_Ref <- read_excel("Data/Moonboard 2019.xlsx", sheet = "Ref Table")


# Generate a "by session" summary data frame
By_Session <- MB19 %>%
  group_by(Date) %>%
  summarize(`Benchmarks Completed` = n(),
            `Average V Grade` = round(mean(`V Grade`), digits = 1),
            `Minimum V Grade` = min(`V Grade`),
            `Maximum V Grade` = max(`V Grade`),
            `Total V Points` = sum(`V Grade`),
            `Session Points` = sum(Points),
            `Grade Distribution` = list(`V Grade`), .groups = "drop") 


# Generate a by Week data frame
By_Week <- MB19 %>%
  mutate(Month = month(Date, label = TRUE),
         Week = week(Date),
         Day = wday(Date, label = TRUE, abbr = TRUE)) %>%
  group_by(Week) %>%
  summarize(`Benchmarks Completed` = n(),
            `Average V Grade` = round(mean(`V Grade`), digits = 1),
            `Minimum V Grade` = min(`V Grade`),
            `Maximum V Grade` = max(`V Grade`),
            `Total V Points` = sum(`V Grade`),
            `Moonboard Points` = sum(Points),
            `Grade Distribution` = list(`V Grade`), .groups = "drop") %>%
  mutate(`Grade Range` = paste0("V", `Minimum V Grade`, " - ", "V", `Maximum V Grade`),
         `Cumulative Benchmarks` = cumsum(`Benchmarks Completed`),
         Week = as.Date(paste(2022, Week, 1, sep = "-"), "%Y-%U-%u")) %>%
  select(Week, `Benchmarks Completed`, `Cumulative Benchmarks`, `Average V Grade`, 
         `Total V Points`, `Grade Range`, `Grade Distribution`, `Moonboard Points`)


# Generate a summary table by grades
By_Grade <- left_join(
  x = MB19_Ref %>% select(Grade, Benchmarks),
  y = MB19 %>%
    mutate(Attempts = case_when(
      Attempts == 1 ~ "Flashed",
      Attempts == 2 ~ "2nd Try",
      Attempts == 3 ~ "3rd Try",
      Attempts > 3 ~ ">3 Tries")) %>%
    group_by(Grade, Attempts) %>%
    summarize(Completed = n(), .groups = "drop") %>%
    pivot_wider(names_from = Attempts, 
                values_from = Completed,
                values_fill = 0) %>%
    mutate(`Total Completed` = rowSums(across(Flashed:`>3 Tries`))),
  by = "Grade"
) %>%
  mutate_if(is.numeric, coalesce, 0) %>%
  mutate(Remaining = Benchmarks - `Total Completed`,
         `Percent Completed` = `Total Completed`/Benchmarks)

```

### Summary Table by Session

```{r}

# By session gt() table
By_Session %>%
  mutate(`Grade Range` = paste0("V", `Minimum V Grade`, " - ", "V", `Maximum V Grade`),
         `Cumulative Benchmarks` = cumsum(`Benchmarks Completed`)) %>%
  select(Date, `Benchmarks Completed`, `Cumulative Benchmarks`, `Average V Grade`, 
         `Total V Points`, `Grade Range`, `Grade Distribution`) %>%
  gt() %>%
  data_color(
    columns = c(`Average V Grade`),
    colors = scales::col_numeric(
      palette = c("#eb633d", "#ebae34", "#b6eb60", "#0bb83c"),
      domain = c(min(By_Session$`Average V Grade`), 
                 max(By_Session$`Average V Grade`))),
    alpha = 0.7) %>%
  data_color(
    columns = c(`Total V Points`),
    colors = scales::col_numeric(
      palette = c("#eb633d", "#ebae34", "#b6eb60", "#0bb83c"),
      domain = c(min(By_Session$`Total V Points`), 
                 max(By_Session$`Total V Points`))),
    alpha = 0.7) %>%
  gt_plt_dist(`Grade Distribution`, 
              line_color = "#89a189", 
              fill_color = "#cce3d3", 
              type = "density",
              fig_dim = c(5, 25)) %>%
  cols_align(
    align = "center",
    columns = c(2:7)) %>%
  cols_width(
    columns = 1 ~ px(125),
    columns = 2:6 ~ px(95),
    columns = 7 ~ px(110)) %>%
  tab_style(
    style = list(cell_text(color = "#2b2b2b")),
    locations = cells_body(columns = 2:7)) %>%
  tab_header(
    title = "Moonboard 2019 Sessions",
    subtitle = paste0(nrow(MB19), "/341 Benchmarks")) %>%
  gt_theme_538() %>%
  opt_align_table_header(align = "center")

```

***

https://rstudio.github.io/leaflet/

- Interactive panning/zooming

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic


### Summary Table by Week

```{r}

# By Week gt() Table
By_Week %>%
  select(-`Moonboard Points`) %>%
  gt() %>%
  data_color(
    columns = c(`Average V Grade`),
    colors = scales::col_numeric(
      palette = c("#eb633d", "#ebae34", "#b6eb60", "#0bb83c"),
      domain = c(min(By_Week$`Average V Grade`), 
                 max(By_Week$`Average V Grade`))),
    alpha = 0.7) %>%
  data_color(
    columns = c(`Total V Points`),
    colors = scales::col_numeric(
      palette = c("#eb633d", "#ebae34", "#b6eb60", "#0bb83c"),
      domain = c(min(By_Week$`Total V Points`), 
                 max(By_Week$`Total V Points`))),
    alpha = 0.7) %>%
  gt_plt_dist(`Grade Distribution`, 
              line_color = "#89a189", 
              fill_color = "#cce3d3", 
              type = "density",
              fig_dim = c(5, 25)) %>%
  cols_align(align = "center", columns = c(2:7)) %>%
  cols_align(align = "left", columns = c(1)) %>%
  cols_width(
    columns = 1 ~ px(130),
    columns = 2:6 ~ px(100),
    columns = 7 ~ px(110)) %>%
  cols_label(Week = "Week of") %>% 
  tab_style(
    style = list(cell_text(color = "#2b2b2b")),
    locations = cells_body(columns = 2:7)) %>%
  tab_header(
    title = "Moonboard 2019 Sessions",
    subtitle = paste0(nrow(MB19), "/341 Benchmarks")) %>%
  gt_theme_538() %>%
  opt_align_table_header(align = "center")

```

***

Some text about this graph 

### By Grade Charts

```{r}

By_Grade %>%
  select(Grade, Flashed, `2nd Try`, `3rd Try`, `>3 Tries`) %>%
  pivot_longer(cols = c(Flashed, `2nd Try`, `3rd Try`, `>3 Tries`), 
               names_to = "Status", 
               values_to = "Count") %>%
  ggplot(aes(x = Grade, y = Count, fill = Status)) +
  geom_col()



By_Grade %>%
  mutate(Flashed = Flashed/Benchmarks, 
         `2nd Try` = `2nd Try`/Benchmarks, 
         `3rd Try` = `3rd Try`/Benchmarks, 
         `>3 Tries` = `>3 Tries`/Benchmarks,
         Remaining = Remaining/Benchmarks) %>%
  pivot_longer(cols = c(Flashed, `2nd Try`, `3rd Try`, `>3 Tries`, Remaining), 
               names_to = "Status", 
               values_to = "Completed") %>%
  mutate(Status = factor(Status, 
                         #levels = c("Flashed", "2nd Try", "3rd Try", ">3 Tries", "Remaining"))) %>%
                         levels = c("Remaining", ">3 Tries", "3rd Try", "2nd Try", "Flashed"))) %>%
  ggplot(aes(x = Grade, y = Completed, fill = Status)) +
  scale_fill_manual(values = c("gray", "#0b7a75", "#22816b", "#388761", "#5e9f39")) +
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  coord_flip() +
  hrbrthemes::theme_ipsum() +
  labs(title = "Percent Completed by Grade")


```



### Bar Charts

```{r}

By_Week %>%
  ggplot(aes(x = Week)) +
  geom_col(aes(y = `Moonboard Points`, fill = `Average V Grade`)) +
  geom_line(aes(y = `Cumulative Benchmarks`*100), size = 2, color = "#4e524f") +
  scale_fill_gradient2(low = "#f72e2e", mid = "#dbd63b", midpoint = 5,  high = "#27ab22") +
  scale_y_continuous(name = "Moonboard Points",
                     sec.axis = sec_axis(~./100, name = "Benchmarks Completed")) +
  theme_classic() +
  labs(title = "Moonboard Points by Session",
       subtitle = "With Cumulative Benchmarks Completed",
       x = "") +
  theme(legend.position = "bottom",
        legend.title = element_text(color = "#0a3636", face = "plain"),
        title = element_text(color = "#0a3636", face = "bold"),
        plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        panel.grid.minor.x = element_blank(),
        panel.grid.minor.y = element_blank(),
        panel.background = element_rect(fill = "#ffffff", color = "#ffffff"),
        axis.text = element_text(face = "bold", color = "#0a3636"),
        axis.title.y.left = element_text(margin = margin(t = 0, r = 12, b = 0, l = 0)),
        axis.title.y.right = element_text(margin = margin(t = 0, r = 0, b = 0, l = 12))) +
  guides(fill = guide_colourbar(barheight = 0.8, title.vjust = 0.9))

```


### Intensity vs Volume Quadrant Chart

```{r}

# Comparison to regular training... a 10-climb pyramid up to max flash grade
Pyramid_10 <- c(7, 7, 7, 7, 8, 8, 8, 9, 9, 10)

# Intensity versus volume quadrant chart
By_Session %>%
  ggplot(aes(x = `Average V Grade`, y = `Total V Points`)) +
  geom_point(alpha = 0.9, size = 2.5) +
  geom_point(aes(x = mean(Pyramid_10), y = sum(Pyramid_10)), size = 3, color = "red") +
  geom_vline(xintercept = mean(By_Session$`Average V Grade`),
             color = "#4d4e4f", linetype = "dashed", size = 0.5) +
  geom_hline(yintercept = mean(By_Session$`Total V Points`),
             color = "#4d4e4f", linetype = "dashed", size = 0.5) +
  scale_x_continuous(limits = c(3, 10), 
                     breaks = c(3:10),
                     labels = c(paste("V", 3:10))) +
  theme_classic() +
  labs(title = "Quadrant Chart", 
       subtitle = "Intensity versus Volume",
       x = "Intensity (Average V Grade)", 
       y = "Volume (Total V Points)") +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.line = element_line(colour = "#4d4e4f", size = 1),
        axis.text = element_text(face = 'bold'),
        panel.background = element_rect(fill = "#f5f4f0"),
        panel.border = element_rect(color = "#4d4e4f", fill = NA, size = 1)) +
  coord_equal(ratio = 1/(max(By_Session$`Total V Points`)/7))

```

***
 
With comparison to a "typical" MB session where I did pyramids up to max flash grade... 4x V7, 3x V8, 2x V9, and 1x V10... shown in red. 

Quadrant 1 (top left )
